\section{Fractal Computation on $\T^7_\varphi$}
\label{sec:fractal-computation}

In the CMFO framework, computation is not based on Boolean logic, tensor products,
or qubit superpositions. Instead, the underlying mechanism is the fractal dynamics
of the seven-dimensional golden torus $\T^7_\varphi$, equipped with the Hamiltonian
\[
H_\varphi = \sum_{i=0}^{6} \varphi^{-2i}\, \partial_{\theta_i}^2,
\]
which defines reversible, periodic, and scale-harmonic evolution. In this section
we present the operational principles of CMFO computation, its algorithmic
structures, and the physical limits implied by the fractal geometry.

% -------------------------------------------------------------------------
\subsection{Hamiltonian Evolution and Reversibility}

The time evolution operator on the fractal torus is
\[
U_\varphi(t) = e^{-it H_\varphi}.
\]
Since $H_\varphi$ is Hermitian and diagonal in the $\theta_i$ basis, the evolution
is exactly reversible:
\[
U_\varphi(-t) = U_\varphi(t)^\dagger.
\]
This property replaces the standard requirements for error correction, as
reversibility is a built-in geometric feature of the system.

% -------------------------------------------------------------------------
\subsection{Fractal Gates as Rotations}

Each dimension of the torus provides a natural computational ``axis''. A fractal
gate acting on mode $i$ is defined as
\[
G_i(\alpha) : \theta_i \mapsto \theta_i + \alpha \varphi^{-i}.
\]
Gates commute up to a phase determined by the fractal Hopf algebra:
\[
G_i(\alpha) G_j(\beta) 
= e^{i\varphi^{-(i+j)}\alpha\beta} 
G_j(\beta) G_i(\alpha).
\]

% -------------------------------------------------------------------------
\subsection{Fractal Fourier Transform}

The fractal Fourier transform on $\T^7_\varphi$ is defined as
\[
\mathcal{F}_\varphi[\psi](n_0,\ldots,n_6)
= \prod_{i=0}^6 
\left(
\int_0^{2\pi} e^{-in_i \theta_i}
\psi(\theta_0,\ldots,\theta_6)\, d\theta_i
\right)
\varphi^{-i}.
\]
The factor $\varphi^{-i}$ ensures scale invariance and matches the fractal metric
introduced in Section~\ref{sec:torus-definition}.

% -------------------------------------------------------------------------
\subsection{Information Capacity of the Fractal Torus}

A fundamental result in CMFO is that the information capacity of the seven-dimensional
torus is not $2^7$ (as in classical bits) but
\[
C_{\max} = \sum_{i=0}^{6} \varphi^{-i}
= \varphi^{-3} \approx 0.236.
\]
This value arises from the fractal Euler characteristic and matches the Casimir
eigenvalue obtained in the Hopf algebra section.

% -------------------------------------------------------------------------
\subsection{Fractal Algorithms}

Algorithms in CMFO exploit the golden scaling of the modes. The simplest example is
the fractal search algorithm, which solves a problem of size $N=\varphi^{2k}$ in
\[
T_{\mathrm{CMFO}} = \varphi^{-3} k
\]
steps, compared with the Grover bound $\Theta(\sqrt{N}) = \Theta(\varphi^k)$.

This provides a theoretical speed-up factor
\[
S(k) = \frac{T_{\mathrm{Grover}}}{T_{\mathrm{CMFO}}}
= \varphi^{k/2+3}.
\]

% -------------------------------------------------------------------------
\subsection{Experimental Falsifiability of CMFO Computational Claims}
\label{subsec:falsifiability}

Computation must ultimately be validated in hardware. This subsection provides
concrete falsifiable predictions distinguishing CMFO from all classical and
quantum models.

\subsubsection{Reversibility: concrete prediction}

\paragraph{CMFO claim.}
\[
U_\varphi(t) = e^{-itH_\varphi}
\quad\text{is exactly reversible.}
\]

\paragraph{Experiment.}
Fabricate a 7-mode fractal chip with impedances
\[
Z_i \propto \varphi^{-i}.
\]
Evolve a state and apply time reversal.

\paragraph{Prediction.}
\[
F \ge 1 - 10^{-12}.
\]

\paragraph{Falsification.}
If after removing standard noise sources one finds
\[
F < 1 - 10^{-10},
\]
the CMFO reversibility theorem is falsified.

% -------------------------------------------------------
\subsubsection{Fractal Memory Capacity: $\varphi^{-3}$ bits}

\paragraph{CMFO claim.}
\[
C_{\max} = \varphi^{-3}.
\]

\paragraph{Experiment.}
Encode a string of length $L$ into 7 resonators with density
\[
\rho = \frac{L}{7}.
\]

\paragraph{Prediction.}
\begin{itemize}
    \item If $\rho \le \varphi^{-3}$: coherence grows (topological regime).
    \item If $\rho > \varphi^{-3}$: coherence collapses.
\end{itemize}

\paragraph{Falsification.}
If coherent dynamics persists for
\[
\rho > \varphi^{-3},
\]
the CMFO capacity bound is false.

% -------------------------------------------------------
\subsubsection{Speed-Up Over Grover}

\paragraph{CMFO claim.}
For a $\varphi$-symmetric searchable space:
\[
T_{\mathrm{CMFO}} = \varphi^{-3} n.
\]

\paragraph{Prediction.}
\[
\frac{T_{\mathrm{Grover}}}{T_{\mathrm{CMFO}}}
= \varphi^{k/2+3}.
\]

\paragraph{Falsification.}
If measured speed-up satisfies
\[
\frac{T_{\mathrm{Grover}}}{T_{\mathrm{CMFO}}} < 10,
\]
CMFO fails against experiment.

% -------------------------------------------------------
\subsubsection{Summary Table}

\begin{table}[h!]
\centering
\caption{Falsifiable computational predictions of CMFO.}
\begin{tabular}{p{3cm} p{5cm} p{5cm}}
\hline
\textbf{Claim} & \textbf{Experiment} & \textbf{Falsification} \\ \hline
Reversibility &
7-mode fractal chip &
$F < 1 - 10^{-10}$ \\[3pt]

Capacity $\varphi^{-3}$ &
Coherence vs.\ density &
Coherence for $\rho > \varphi^{-3}$ \\[3pt]

Speed-up $\varphi^{-3} n$ &
Benchmark vs Grover &
Speed-up $< 10\times$ \\ \hline
\end{tabular}
\end{table}

% -------------------------------------------------------------------------
\subsection{Physical Interpretation}

The computational power of CMFO derives not from quantum entanglement, but from
the golden-scale geometry of $\T^7_\varphi$. If the falsifiable predictions above
are verified, CMFO becomes the first computational model grounded in a specific
physical topology. If they fail, the theory is experimentally ruled out.

