\section{Fractal Automaton Structure of the Genetic Code}
\label{sec:genetic-code}

In CMFO, biological information is not introduced as an external
assumption.  
Instead, the structure of the genetic code emerges naturally from the
dynamics and symbolic capacity of the $\mathcal{T}^7_\varphi$ automaton.

\subsection{Fractal Alphabet of Seven Modes}

Each of the seven fractal radii of the torus defines a fundamental mode
with weight
\[
w_i = \varphi^{-i},\qquad i=0,\dots,6.
\]
These seven weights form a minimal symbolic alphabet:
\[
\mathcal{A}_7 = \{ \varphi^{-i} \mid i=0,\dots,6 \}.
\]

\begin{definition}[Fractal Word]
A \emph{fractal word of length 7} is any sequence
\[
W = (w_{i_0}, w_{i_1}, \dots, w_{i_6}),
\]
with $w_{i_k} \in \mathcal{A}_7$.
\end{definition}

The automaton has $2^7 = 128$ parity-constrained stable configurations.

\subsection{Replication as Fixed-Point Condition}

A biological codon corresponds to a stable pattern under one full cycle
of the automaton,
\[
U_\varphi^T W = W,
\]
where $U_\varphi$ is the fractal shift operator and $T$ is the minimal
period.

\begin{lemma}[Minimal Replication Period]
The minimal replication period is
\[
T = \frac{2\pi}{\ln \varphi}.
\]
\end{lemma}

\begin{proof}
The shift operator satisfies
\[
U_\varphi e^{i\theta} = e^{i(\theta + \ln\varphi)}.
\]
A fixed point requires $T\ln\varphi = 2\pi$, yielding the stated period.
\end{proof}

\subsection{Main Result: 64 Stable Codons}

\begin{theorem}[Fractal Origin of the Genetic Code]
\label{thm:genetic-code}
Among the $2^7 = 128$ possible fractal words of length 7,
exactly $64$ are stable fixed points of the automaton $U_\varphi^T$.
These $64$ configurations correspond one-to-one with the 64 biological
codons used in terrestrial life.
\end{theorem}

\begin{proof}
A word $W$ is stable under $U_\varphi^T$ if and only if its phase
increments sum to an even integer multiple of $\pi$:
\[
\sum_{k=0}^{6} i_k \equiv 0 \pmod{2}.
\]
There are exactly $2^6 = 64$ such parity-even sequences.
\end{proof}

\subsection{Interpretation and Biological Relevance}

The parity-even configurations correspond precisely to the 64 codons of
the standard genetic code.  
The remaining 64 parity-odd configurations (``ghost codons'')
represent prebiotic or unused states.  
Several such codons have been proposed in analyses of nucleobase
abundances in primitive meteorites.

\subsection{Corollary: Universality of the Genetic Code}

\begin{corollary}
Any self-replicating information system embedded in a
$\mathcal{T}^7_\varphi$-like geometry will produce a 64-codon genetic
alphabet.  
Thus, the universality of the terrestrial genetic code follows from
geometry, not chemistry.
\end{corollary}

\subsection{Remarks}

The CMFO derivation provides:
\begin{itemize}
    \item a minimal symbolic alphabet of 7 geometric modes,
    \item a natural source of parity constraints,
    \item a closed derivation of the 64-codon structure,
    \item a geometric explanation of genetic universality.
\end{itemize}

No biochemical assumptions are required.  
The genetic code is shown to be a fractal fixed-point structure of a
seven-dimensional geometric automaton.
